Appendix

### 2020-03-02 manuscript/appendix.Rmd
use log10_x scale

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tn))) + 
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)"), 
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tp))) +
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)")
)

>>>>

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10()
)
